\documentclass[a4paper, oneside]{article}
\usepackage{amsmath}
\usepackage{xspace}
\usepackage{tabularx}
\usepackage{url}

\usepackage{enumitem}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{float}

\usepackage[margin=3cm]{geometry}

\usepackage{etoolbox}

\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{booktabs}

\newcommand\st{\textsuperscript{st}\xspace}
\newcommand\nd{\textsuperscript{nd}\xspace}
\newcommand\rd{\textsuperscript{rd}\xspace}
\newcommand\nth{\textsuperscript{th}\xspace} %\th is taken already

\newtoggle{outputAnswers}

% Toggle whether or not to include answers to homework questions.
 \toggletrue{outputAnswers}
%\togglefalse{outputAnswers}


\newcommand{\assignment}[0]{assignment\xspace}
\newcommand{\assignments}[0]{assignments\xspace}
\newcommand{\Assignment}[0]{Assignment\xspace}
\begin{document}
	\title{Computer Vision \& Imaging/ Robot Vision - Formative task}
	\date{\today}
	
	\maketitle
    \begin{center}
        \Large
        Answer Sheet
    \end{center}
    \begin{description}
    	\item[Question 1] \emph{Load the League of Legends Champions stats data from \texttt{data.csv}. Normalise the data and apply principal component analysis to calculate the principal component coefficients. Visualise the first and second principal components with a loading plot, explain the meaning of a loading plot, and describe what kind of information you can obtain from the loading plot.}
    	\item[Answer]
    	\item[Question 2] \emph{Alternatively, use a bar chart to illustrate the principal component coefficients, and compare it with the loading plot: what's the pros and cons of a loading plot and a bar chart?}
    	\item[Answer]
    	\item[Question 3] \emph{Calculate total variance of all principal components, and visualise the accumulative variance with each principal component. Describe how much does the first two principal components explained from the data.}
    	\item[Answer]
    	\item[Question 4] \emph{Perform dimensionality reduction to the data, and visualise the data on a score plot using the first two principal components. Use different color to distinguish champions with different type. Judging by the champions' types, how well does PCA explain the given dataset?}
    	\item[Answer]
	\end{description}
\end{document}
